---
title: "Indice de Rand"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Indice de Rand}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
library(Rindex)
knitr::opts_chunk$set(collapse = T, comment = "#>")
```

This vignette will be about Rand's index and its utilization. For that, we will 
explain how it works with practical examples. Here, we will change 4 variables : 
Mu, Sigma, n.norms and the number of observations. In this vignette
like the Jaccard one, we will keep the same methods to be able to see differences between 
each index. 

In this vignette, "ward.D" and "complete" will be our tested methods.

# Reference

This example will be a reference for the 4 examples that will follow. With this, 
we will be able to see the variation of each of our variables.

```{r}
n = 4
Mu = 5 
sigm = 2       
nb_obs= 100

#creation of the data frame and implementing it in our function clustering
df <- clustering(dataframe = norme(n.norms = n,n = nb_obs,mu = Mu,sigma = sigm),
                 k = 3)           



rand(dataframe = df,
        method1 = "ward.D",
        method2 = "complete")    #choice of method for our rand function 

#creation of the graphics to compare the similarities
plot(df$x,df$y,col=df$ward.D, main="ward.D method")     
plot(df$x,df$y,col=df$complete, main="complete method")
```


