---
title: "Indice de Jaccard"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Indice de Jaccard}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
library(Rindex)
knitr::opts_chunk$set(collapse = T, comment = "#>")
```

This vignette will be about Jaccard index and its utilization. For that, we will 
explain how it works with practical examples. Here, we will change 4 variables : 
Mu, Sigma, n.norms and the number of observations. In this vignette
like the Rand one, we will keep the same methods to be able to see differences between 
each index.

In this vignette, "single" and "centroid" will be our tested methods.

# Reference

This example will be a reference for the 4 examples that will follow. With this, 
we will be able to see the variation of each of our variables.

```{r}
n = 4
Mu = 5 
sigm = 2       
nb_obs = 100

#creation of the data frame and implementing it in our function clustering
df <- clustering(dataframe = norme(n.norms = n,n = nb_obs,mu = Mu,sigma = sigm),
                 k = 3)           



jaccard(dataframe = df,
        method1 = "ward.D",
        method2 = "complete")    #choice of method for our jaccard function 

#creation of the graphics to compare the similarities
plot(df$x,df$y,col=df$ward.D, main="ward.D method")     
plot(df$x,df$y,col=df$complete, main="complete method") 
```

# Example 1

Here, we are focusing on Mu : 
```{r}
Mu = 10 
n = 4           #Constant for this example
sigm = 2        #Constant for this example 
nb_obs = 100    #Constant for this example

#creation of the data frame and implementing it in our function clustering
df <- clustering(dataframe = norme(n.norms = n,n = nb_obs,mu = Mu,sigma = sigm),
                 k = 3)           



jaccard(dataframe = df,
        method1 = "ward.D",
        method2 = "complete")    #choice of method for our jaccard function 

#creation of the graphics to compare the similarities
plot(df$x,df$y,col=df$ward.D, main="ward.D method")     
plot(df$x,df$y,col=df$complete, main="complete method") 
```

# Example 2

Same case with sigma :
```{r}
Mu = 5          #Constant for this example 
n = 4           #Constant for this example
sigm = 10 
nb_obs = 100    #Constant for this example

#creation of the data frame and implementing it in our function clustering
df <- clustering(dataframe = norme(n.norms = n,n = nb_obs,mu = Mu,sigma = sigm),
                 k = 3)           



jaccard(dataframe = df,
        method1 = "ward.D",
        method2 = "complete")    #choice of method for our jaccard function 

#creation of the graphics to compare the similarities
plot(df$x,df$y,col=df$ward.D, main="ward.D method")     
plot(df$x,df$y,col=df$complete, main="complete method")  
```

# Example 3

For n :  
```{r}
Mu = 5          #Constant for this example
n = 16          
sigm = 2        #Constant for this example 
nb_obs= 100    #Constant for this example

#creation of the data frame and implementing it in our function clustering
df <- clustering(dataframe = norme(n.norms = n,n = nb_obs,mu = Mu,sigma = sigm),
                 k = 3)           



jaccard(dataframe = df,
        method1 = "ward.D",
        method2 = "complete")    #choice of method for our jaccard function 

#creation of the graphics to compare the similarities
plot(df$x,df$y,col=df$ward.D, main="ward.D method")     
plot(df$x,df$y,col=df$complete, main="complete method") 
```

# Example 4

And finally, with our number of observations : 
```{r}
Mu = 5          #Constant for this example
n = 4           #Constant for this example
sigm = 2        #Constant for this example 
nb_obs= 500

#creation of the data frame and implementing it in our function clustering
df <- clustering(dataframe = norme(n.norms = n,n = nb_obs,mu = Mu,sigma = sigm),
                 k = 3)           



jaccard(dataframe = df,
        method1 = "ward.D",
        method2 = "complete")    #choice of method for our jaccard function 

#creation of the graphics to compare the similarities
plot(df$x,df$y,col=df$ward.D, main="ward.D method")     
plot(df$x,df$y,col=df$complete, main="complete method") 
```
