---
title: "Indice de Jaccard"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Indice de Jaccard}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(Rindex)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(collapse = T, comment = "#>")
```

This vignette will be about Jaccard index and its utilization. For that, we will 
explain how it works with practical examples. Here, we will change 4 variables : 
Mu, Sigma, n.norms and the number of observations. In this vignette
like the Rand one, we will keep the same methods to be able to see differences between 
each index.

In this vignette, "single" and "centroid" will be our tested methods.

# Reference

This example will be a reference for the 4 examples that will follow. With this, 
we will be able to see the variation of each of our variables.

```{r}
n = 4
Mu = 5 
sigm = 2       
nb_obs= 1000

df <- clustering(dataframe = norme(n.norms = n,n = nb_obs,mu = Mu,sigma = sigm),
                 k = 3)           #creation of the data frame and implementing it 
                                  #in our function clustering

df1 <- df %>% 
  summarise(count=n())

df <- cbind(df,df1)

jaccard(dataframe = df,
        method1 = "single",
        method2 = "centroid")    #choice of method for our rand function 

ggplot(df) +                    
  aes(x,y) + 
geom_point(aes(color=centroid))  #creation of the graphic 
```

# Example 1

Here, we are focusing on Mu : 
```{r}
Mu = 10 
n = 4           #Constant for this example
sigm = 2        #Constant for this example 
nb_obs= 1000    #Constant for this example

df <- clustering(dataframe = norme(n.norms = n,n = nb_obs,mu = Mu,sigma = sigm),
                 k = 3)           #creation of the data frame and implementing it 
                                  #in our function clustering

df1 <- df %>% 
  summarise(count=n())

df <- cbind(df,df1)

jaccard(dataframe = df,
        method1 = "single",
        method2 = "centroid")    #choice of method for our rand function 

ggplot(df) +                    
  aes(x,y) + 
geom_point(aes(color=centroid))  #creation of the graphic 
```

# Example 2

Same case with sigma :
```{r}
Mu = 5          #Constant for this example 
n = 4           #Constant for this example
sigm = 10 
nb_obs= 1000    #Constant for this example

df <- clustering(dataframe = norme(n.norms = 4,n = nb_obs,mu = Mu,sigma = sigm),
                 k = 3)           #creation of the data frame and implementing it 
                                  #in our function clustering

df1 <- df %>% 
  summarise(count=n())

df <- cbind(df,df1)

jaccard(dataframe = df,
        method1 = "single",
        method2 = "centroid")    #choice of method for our rand function 

ggplot(df) +                    
  aes(x,y) + 
geom_point(aes(color=average))  #creation of the graphic 
```

# Example 3

For n :  
```{r}
Mu = 5          #Constant for this example
n = 16          #Constant for this example
sigm = 2        #Constant for this example 
nb_obs= 1000

df <- clustering(dataframe = norme(n.norms = 4,n = nb_obs,mu = Mu,sigma = sigm),
                 k = 3)           #creation of the data frame and implementing it 
                                  #in our function clustering

df1 <- df %>% 
  summarise(count=n())

df <- cbind(df,df1)

jaccard(dataframe = df,
        method1 = "single",
        method2 = "centroid")    #choice of method for our rand function 

ggplot(df) +                    
  aes(x,y) + 
geom_point(aes(color=centroid))  #creation of the graphic 
```

# Example 4

And finally, with our number of observations : 
```{r}
Mu = 5          #Constant for this example
n = 4           #Constant for this example
sigm = 2        #Constant for this example 
nb_obs= 100

df <- clustering(dataframe = norme(n.norms = 4,n = nb_obs,mu = Mu,sigma = sigm),
                 k = 3)           #creation of the data frame and implementing it 
                                  #in our function clustering

df1 <- df %>% 
  summarise(count=n())

df <- cbind(df,df1)

jaccard(dataframe = df,
        method1 = "single",
        method2 = "centroid")    #choice of method for our rand function 

ggplot(df) +                    
  aes(x,y) + 
geom_point(aes(color=centroid))  #creation of the graphic 
```
